---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  tidy = "styler"
)
```

# edmdown

<!-- badges: start -->
<!-- badges: end -->

The goal of edmdown is to provide a reproducible template for the Journal of Educational Data Mining using R Markdown in multiple formats such as pdf, gitbook, and Word.

## Installation

`edmdown` is currently under development on GitHub. Please install and test the package as follows:

```{r installation, eval = FALSE}
if(!require(remotes)) {
install.packages("remotes")
}

remotes::install_github('jooyoungseo/edmdown')
```

## Example

This is a basic example which shows you how to use `edmdown` package.

While other formats are usable, `pdf` output is fully supported at this moment.

```{r example, eval = FALSE}
## Loading package:
library(edmdown)

## Making a template using RStudio; do the following if you are a non-RStudio user:
rmarkdown::draft(file = "my_article", 
   template = "jedm_article", 
   package = "edmdown"
)

# After editing, use the bookdown knit button in RStudio; if you don't use RStudio, do the following in your R console:
bookdown::render_book("my_article.Rmd", output_format = "all")
```
